Results

### 2018-03-30 02_analysis.Rmd
Use gray instead of black

  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
    geom_bar(stat = "identity", fill = "black") +
    theme_spark()

@@

  fig_hist <- ggplot(as.data.frame(x), aes(x = x)) +
    geom_histogram(fill = "black", binwidth = 10) +
    theme_spark()

>>>>

  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
    geom_bar(stat = "identity", fill = "grey50") +
    theme_spark()

@@

  fig_hist <- ggplot(as.data.frame(x), aes(x = x)) +
    geom_histogram(fill = "grey50", binwidth = 10) +
    theme_spark()
